\Huge \scshape \fontfamily{pbk}\fontsize{50}{40}\selectfont The Dark \LaTeX{} \\ \medskip \normalfont \medskip\Huge An Example of the dndbook Class

### 2021-09-05 fancy-example.tex
Ported the hardcover book style from ryumaou, with an optional example (fancy-example.tex) of how to use those features (rather than having a bunch of stuff commented out in example.tex)

\documentclass[letterpaper,twocolumn,openany,nodeprecatedcode]{dndbook}

@@

\usepackage[utf8]{inputenc}
\usepackage[singlelinecheck=false]{caption}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{shortvrb}
\usepackage{stfloats}
\usetikzlibrary{intersections} % Required for ornamentedtabular

@@

\title{
  \Huge \scshape \fontfamily{pbk}\fontsize{50}{40}\selectfont
  The Dark \LaTeX{} \\
  \medskip
  \normalfont
  \medskip\Huge
  An Example of the dndbook Class
}
\author{The rpgTeX Team}
\date{}

\begin{document}

@@

\maketitle

@@

>>>>

\documentclass[letterpaper,twocolumn,openany,fancy,nodeprecatedcode]{dndbook}

@@

\usepackage[utf8]{inputenc}
\usepackage[singlelinecheck=false]{caption}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{shortvrb}
\usepackage{stfloats}
\usepackage{url}
\usetikzlibrary{intersections} % Required for ornamentedtabular

@@

% title is not used with the rpgMakeCover and other options below:
\title{
  \Huge \scshape \fontfamily{pbk}\fontsize{50}{40}\selectfont
  The Dark \LaTeX{} \\
  \medskip
  \normalfont
  \medskip\Huge
  An Example of the dndbook Class
}
\author{The rpgTeX Team}
\date{}

\begin{document}
\rpgMakeCover[
    image = img/front-cover,
    logo = img/logo,
    title = \DndFontTitle\DndTitleContour{RPG Game Book Template},
    subtitle = \DndFontSubtitle\DndSubtitleContour{An example of the dndbook class,\newline styled like a hardcover book.},
]

\rpgMakeTitle[
    title = {RPG Game Book Template},
    subtitle = {An example of the dndbook class,\newline styled like a hardcover book.},
    author = {Author McAuthorson},
    credits = {Copyright © \the\year{} Author McAuthorson\newline\vspace{2ex} Credits:\newline Original fork: \small{\url{https://github.com/rpgtex/DND-5e-LaTeX-Template}}\newline Hardcover style adapted from: \small{\url{https://github.com/ryumaou/RPG-LaTeX-Template-With-Cover}}}
]

@@

@@

\rpgMakeBackCover[
    image = img/back-cover,
    logo = img/logo,
    title = \DndFontTitle\DndTitleContour{RPG Game Book Template},
    subtitle = \DndFontSubtitle\DndSubtitleContour{An example of the dndbook class,\newline styled like a hardcover book.},
    blurbtext = {A blurb or quip to describe the book\\Gather your party!}
]
